Exploring dimensions of biodiversity in Japanese ferns

### 2020-07-15 presentations/bsa_2020-07-27/index.Rmd
Update slides

.footnote[.small[Photos A. Ebihara]]

@@

.pull-right-wide[
<img src="images/japan_intro_cropped.png" alt="drawing" height="580"/>
]

@@

---
## Compare raw values to random expectation with <u>**S**</u>tandard <u>**E**</u>ffect <u>**S**</u>ize

PD is mostly clustered throughout

@@

.footnote[Trendline: GAM with cubic splines]
---
background-position: 40% 50%
background-image: url(images/rpd.png)
background-size: contain

@@

- Refugium

@@

- Recently diverged lineages

@@

---
## Compare branch lengths with <u>**R**</u>elative <u>**P**</u>hylogenetic <u>**D**</u>iversity

RPD is high in the N and S

@@

.footnote[Trendline: GAM with cubic splines `r NoCite(bib, "Faith1992")`]
---
## <u>**R**</u>elative <u>**F**</u>unctional <u>**D**</u>iversity: functional analog of RPD

Southern islands have high RFD

@@

.footnote[Trendline: GAM with cubic splines]
---
## Phylogenetic endemism: PD weighted by range size

Southern islands are hotspots of endemism

@@

>>>>

.footnote[.small[Photos: A. Ebihara]]

@@

.pull-right-wide[
<img src="images/japan_intro.png" alt="drawing" height="580"/>
]

@@

---
## SES of PD is mostly clustered throughout

@@

.footnote[Trendline: GAM with cubic splines]
---
background-position: 40% 50%
background-image: url(images/RPD.png)
background-size: contain

@@

- Refugia

@@

- Recently speciation

@@

---
## RPD is high in the north and south

@@

.footnote[Trendline: GAM with cubic splines `r NoCite(bib, "Faith1992")`]
---
## Southern islands have high RFD

(RFD = functional analog of RPD)

@@

.footnote[Trendline: GAM with cubic splines]
---
## Southern islands are hotspots of endemism

(Phylogenetic endemism = PD weighted by range size)

@@

---
class:: big-margin

# Acknowledgements

.center[
<img src="images/pags-logo.png" alt="drawing" width="600"/>

<img src="images/shida-no-kai-logo.png" alt="drawing" height="120"/>

Members of the Iwasaki Lab (The University of Tokyo)

Eric Schuettpelz (Smithsonian Institution)

Alexander White (Smithsonian Institution)
]
